---
title: "ENCODE-DREAM in vivo Transcription Factor Binding Site Prediction Challenge"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Competition:  
**source: https://www.synapse.org/#!Synapse:syn6131484/wiki/402033 **  
Install meme suite to use **ama** to calculate tf scores along the DNA.

Define a **base** directory and, on top of that, a **writeup** directory.

Copy all the github files in the **base/writeup/** directory.

Copy these data in the **base** directory:  

####Extract all files

```{r, engine = 'bash', eval = FALSE}
training_data.ChIPseq.tar
training_data.DNASE_wo_bams.tar
training_data.RNAseq.tar
training_data.annotations.tar
```
***

Under the ***writeup*** dirctory, at the beginning of ***'functions_for_main_program.R'***
set the variables **tf**, for what transcription factor will be assessed and the **base** 
directory.

In annotations directory, use bedtools to extract fasta from bed coordinates:
```{r, engine = 'bash', eval = FALSE}
 bedtools getfasta -fi hg19.genome.fa -bed test_regions.blacklistfiltered.bed -fo test_regions.blacklistfiltered.fa
  ```
```{r, engine = 'bash', eval = FALSE}
 bedtools getfasta -fi hg19.genome.fa -bed ladder_regions.blacklistfiltered.bed -fo ladder_regions.blacklistfiltered.fa
```
## Get background file for meme suite (ama) in the writeup directory:
```{r, engine = 'bash', eval = FALSE}

 fasta-get-markov ../annotations/hg19.genome.fa hg19markov.bkg
```

Then source the file 'functions_for_main_program.R'
```{r, eval=FALSE}
source('functions_for_main_program.R')
```
As it is stated in the **main.R** execute the function
**run_execbash_sh_on_tf_folder_after_this(tf)**
and, using the terminal(I used ubuntu xenial), go to the folder
**'base/writeup/results/tf'** where the **tf** was defined in the beginning
and execute execbash.sh

***  
#####Important
Execute execbash.sh on the tf directory, to get the file
with the TF score using the meme suit
 
***

## Running Machine Learning and Generating Files to Submit (Leaderboard and Test, if any)
At this point, everything shoud work fine, generating the files to submit in the 
respective **tf** directory:
```{r ,eval=FALSE}
preprocess_writeup(tf)
dd<-load_features(tf)
#machine learnig section
for(e in c(leaderboard,test)){
  xgscore<-xgbtrain(e)
  rfscore<-rftrain(e)
  fcs(xgscore,rfscore,e)
}
```
Name: maximus

Ricardo Paixao dos Santos  

Prof. Katlin Brauer Massirer, Ph.D.  

Lab of RNA and microRNA Regulation in Disease,  

Center for Molecular Biology and Genetic Engineering  

University of Campinas, UNICAMP

Av Candido Rondon, 400 Campinas,13083-875, Brazil  


*ps: For now, this codes are enouth to get file to submit.*   
*Later I can add some graphics and insights.*  
