---
title: WRITE UP of ENCODE-DREAM in vivo Transcription Factor Binding Site Prediction
  Challenge
output: html_document
bibliography: rf.bib
csl: cell.csl
#http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html
---
Name: maximus          
Ricardo Paixao dos Santos     
Prof. Katlin Brauer Massirer, Ph.D.  
Lab of RNA and microRNA Regulation in Disease,                    
Center for Molecular Biology and Genetic Engineering                     
University of Campinas, UNICAMP         
Av Candido Rondon, 400 
Campinas,13083-875, Brazil   

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Introduction
   The model consist of a ensemble of 100 RandomForest [@Breiman2001] (that already is a ensemble of Decision Trees),
combined with xgboost [@xg] predictions. The choice of this approach had the aim to avoid overfitting.
   Random Forests have the property of reducing variance keeping the bias low [@Breiman2001], which 
gives to this algorithm a good power of generalization, fundamental on unseen data as in this competition, 
and relativelly easier to tune its parameters.
   Gradient Boosting Machine has competitive perfomace, outperforming RandomForests in some problems. Since their arquitetures are differents, their combination can improve the predictive performance, a fact observed in [@Marbach2012].

## Methods 

* ###Parameters
   Each one of the 100 RandomForests models were set on the same parameters and their predictions were combined with 
simple mean. Tunning was made using 3-fold cross validation on some trainning sets.
   The GBM was used with the R package XGBoost and the parameters set using the xgb.cv (cross validation)
   For each trainning and test set,we used the information from ChIP-Seq, DNASE fold coverage, DNASE peaks conservative fold, annotations from Ensembl and the average and maximum values motifs scores.
   It was not possible to use the DNAshape data because of the amount of RAM memory needed and time necessary to process this task.
   
* ###PreProcessing
  The motifs scores were calculated with the meme suite (software ame [@McLeay2010]). These scores and the parameter maxfc (max fold change dnase) were log10 transformed. These parameters, and others from DNASE experiments were obtained
with both the average and maximum values. 
Once the randomForest has scale problems, all numeric variables was scaled to mean zero
and standard deviation 1. 


```{r include=FALSE, cache=FALSE}
library(ggplot2)
```



####Prediction Error(MSE) vs Rsquared of 100 RandomForest to Predict 'ATF2' Binding Sites


```{r pressure, echo=FALSE}
load(file='atf2ra.RData')
df<-data.frame(r.squared=y[,2],prediction.error=x[,2])
m <- ggplot(df, aes(x = r.squared, y = prediction.error)) +  geom_point()
m + geom_point(aes(colour = prediction.error)) + scale_colour_gradient(low = "blue") + theme_bw()

```


## References
